ms_results

### 2023-04-28 ms_results.Rmd

Since direct measurements of human consumption (e.g. dietary intake) are not collected globally, consumption is generally represented by apparent consumption. Apparent consumption is generally calculated as production plus imports minus exports and waste. Trade is therefore central to estimating consumption and historically limited understanding of aquatic food consumption patterns. By estimating species level trade, we are able to estimate apparent consumption of aquatic foods by species, production method, and geographical origin.

@@

Since we estimate exports from domestic and foreign sources, we can track changes in reliance on foreign sourced products. Globally the share of consumption that is foreign-sourced increased modestly, from `r signif(foreign_consumption_start, digits = 3)`% to `r signif(foreign_consumption_end, digits = 3)`% (Fig 3c). Patterns vary greatly across regions with Asia and S America dominated by domestic supply (`r signif(foreign_consumption_region %>% filter(year == 2019, region == "Asia", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% and `r signif(foreign_consumption_region %>% filter(year == 2019, region == "South America", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% foreign in 2019, respectively), but Europe dominated by foreign supply (`r signif(foreign_consumption_region %>% filter(year == 2019, region == "Europe", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% foreign in 2019) (Fig 3d). High reliance on foreign-sourced foods can pose a food security risk (Baer-Nawrocka and Sadowski 2019; Kummu et al. 2020), though it is not clear the extent to which these risks exist across aquatic foods. Nevertheless, countries have enacted policies to protect domestic supplies, including developing food stocks and subsidizing domestic food production (Wood et al. 2023). The United States used foreign dependence on aquatic foods as a motivation for a suite of policy changes to boost domestic production, including expanding aquaculture production and opening marine protected areas to fishing (Gephart et al. 2019).

>>>>

Since direct measurements of human food consumption (e.g., dietary intake) are not collected globally, it is often represented by apparent consumption. Apparent consumption is calculated as production plus imports minus exports and waste. Trade is therefore central to estimating consumption and has historically limited understanding of aquatic food consumption patterns. By estimating species level trade, we estimate apparent consumption of aquatic foods by species/species group, production method, and geographical origin.

@@

Estimating the foreign versus domestic source of consumption requires identifying the share of production retained in the country and tracking products that undergo foreign processing but are imported again. By estimating the source of traded aquatic foods, we can therefore track changes in reliance on foreign-sourced products. Globally the share of foreign-sourced consumption increased modestly, from `r signif(foreign_consumption_start, digits = 3)`% in 1996 to `r signif(foreign_consumption_end, digits = 3)`% in 2019 (Fig 3c). However, patterns vary greatly across regions with Asia and South America dominated by domestic supply (`r signif(foreign_consumption_region %>% filter(year == 2019, region == "Asia", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% and `r signif(foreign_consumption_region %>% filter(year == 2019, region == "South America", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% foreign in 2019, respectively), ), but countries in Europe dominated by foreign supply (`r signif(foreign_consumption_region %>% filter(year == 2019, region == "Europe", supply_source == "foreign") %>% pull(supply_percent), digits = 2)`% foreign in 2019) (Fig 3d). High reliance on foreign-sourced foods can pose a food security risk (Baer-Nawrocka and Sadowski 2019; Kummu et al. 2020), though it is not clear the extent to which these risks exist across aquatic foods. Nevertheless, countries have enacted policies to protect domestic supplies, including developing food stocks and subsidizing domestic food production (Wood et al. 2023). The United States used foreign dependence on aquatic foods as a motivation for a suite of policy changes to boost domestic production, including expanding aquaculture production and opening marine protected areas to fishing (Gephart et al. 2019).
